---
title: "Predicting Petal Length in Iris'"
author: "Me"
date: "2023-06-11"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the project

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.

2. Deploy the application on Rstudio's shiny server

3. Share the application link by pasting it into the provided text box

4. Share your server.R and ui.R code on github

## How to use the app

- The app was created in R using the Shiny package (this slideshow was also created in R using R Markdown). 

- The app's purpose is to predict the petal length of iris' based on it's sepal length.

- the data used to train the prediction model was the 'iris' data, present within R

- you can find the app here: 

## Example of the iris data

```{r}
head(iris)
```

## Iris sepal and petal width plotted

```{r}
plot(iris$Sepal.Length, iris$Petal.Length, xlab = "Sepal Length", 
             ylab = "Petal Width", bty = "n", pch = 16,
             xlim = c(3, 7), ylim = c(0, 7))
```

